calibration

### 2016-06-02 Rmd/calibration.Rmd
Full draft as of 1 June 2016

---
title: "calibration"
author: "Lyndon Estes"
date: "January 8, 2016"
output: 
  html_document:
    toc: yes
    fig_caption: true
---

@@

```{r, eval=FALSE}
# Read in and clean-up calibration data
cal <- data.table(read_excel(fp(p_dat, "merged_calibration.xlsx")))
cal[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
cal[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
names(cal)
dropnm <-  c("V29")#, "V31", "journal", "exclusion reason", "sensitivity")
cal[, c(dropnm) := NULL]

# check data types
for(j in names(cal)[8:24]) set(cal, j = j, value = as.numeric(cal[[j]]))

# use NA in n_sites as indicator that study was excluded
cal[, inout := ifelse(is.na(n_sites), 0, 1)]  
# write.csv(cal, file = fp(p_dat, "merged_calibrationf.csv"))
```

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
names(cal)
cal[, c("notes", "V29") := NULL]
for(j in names(cal)[c(4:5, 10:24)]) {
  set(cal, j = j, value = as.numeric(cal[[j]]))
}
# length(which(is.na(cal$feature)))

@@

Others need to fix their study duration figures. Paul on paleo one in calibration, Choi, Chang, etc in main set.  [Ahmed remaining]

>>>>

---
title: "calibration"
author: "Lyndon Estes"
date: "January 8, 2016"
output: 
  html_document:
    toc: yes
    number_sections: true
    toc_depth: 3
    fig_caption: true
---

@@

```{r, eval=FALSE, echo = FALSE}
# Read in and clean-up calibration data
# cal <- data.table(read_excel(fp(p_dat, "merged_calibration.xlsx")))
# cal[, DOI := gsub("DOI:|doi:|DOI: |doi: |DOI ", "", DOI)]
# cal[, DOI := gsub("\\s", "", DOI)]  # remove DOI and whitespace
# names(cal)
# dropnm <-  c("V29")#, "V31", "journal", "exclusion reason", "sensitivity")
# cal[, c(dropnm) := NULL]
# 
# # check data types
# for(j in names(cal)[8:24]) set(cal, j = j, value = as.numeric(cal[[j]]))
# 
# # use NA in n_sites as indicator that study was excluded
# cal[, inout := ifelse(is.na(n_sites), 0, 1)]  
# write.csv(cal, file = fp(p_dat, "merged_calibrationf.csv"))
```

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationffff.xlsx")))
names(cal)
cal[, c("notes", "V30") := NULL]
for(j in names(cal)[c(4:5, 10:24)]) {
  set(cal, j = j, value = as.numeric(cal[[j]]))
}
# length(which(is.na(cal$feature)))

@@

Others need to fix their study duration figures. Paul on paleo one in calibration, Choi, Chang, etc in main set.  [DONE]
